---
title: "COMPSCIX 415.2 Homework 9/Final"
author: "Rachel Hollowgrass"
date: "4/3/2018"
output:
 html_document:
  self_contained: true
---

```{r, warning = FALSE, message = FALSE}
# load packages
library(tidyverse)
library(modelr)
library(rpart)
library(partykit)
library(randomForest)
```


### Bootstrapping (10 points)  

<ol start="1">
  <li>Follow these steps:</li>
</ol>

<ul>
  <li>Load the train.csv dataset into R.</li>
  <li>Convert all <code>character</code> columns into unordered <code>factors</code>.</li>
  <li>Convert the <code>Survived</code> column into an unordered factor because it is loaded as an integer by default.</li>
  <li>Take a <code>glimpse</code> of your data to confirm that all of the columns were converted correctly.</li>
</ul>

```{r}
file_path <- '../data/homework9/train.csv'
train <- read_csv(file_path)
train
```


```{r}
# Character vars:
# Name = col_character(),
# Sex = col_character(),
# Ticket = col_character(),
# Cabin = col_character(),
# Embarked = col_character()

# Not factoring Name, Ticket or Cabin because each instance is unique or almost unique and would not factor well.
# Factors are unordered by default, so no need to add ', ordered = FALSE' after the vector assignment.

# Survived is not a continous variable, so make a factor for it.
train <- train %>% mutate(Survived = 
  factor(case_when(
                  Survived == 1 ~ 'True',
                  Survived == 0 ~ 'False'
                  ),
            levels = c('True', 'False')
         )
  )

# Sex is also not a continous variable, so make a factor for it.
train <- train %>% mutate(Sex = 
  factor(case_when(
                  Sex == "male" ~ 'Man',
                  Sex == "female" ~ 'Woman'
               ),
            levels = c('Man', 'Woman')
         )
  )

# Pclass is also not a continous variable, so make a factor for it.
train <- train %>% mutate(Pclass = 
  factor(case_when(
                  Pclass == 1 ~ 'First',
                  Pclass == 2 ~ 'Second',
                  Pclass == 3 ~ 'Third'
                  ),
            levels = c('First', 'Second', 'Third')
         )
  )

# Embarked is also not a continous variable, so make a factor for it.
# S = Southampton, England
# C = Cherbourg, France
# Q = Queenstown, Ireland
# Never arrived at New York

train <- train %>% mutate(Embarked = 
  factor(case_when(
                  Embarked == "C" ~ 'Cherbourg',
                  Embarked == "Q" ~ 'Queenstown',
                  Embarked == "S" ~ 'Southampton'
                  ),
            levels = c('Southampton', 'Cherbourg', 'Queenstown')
         )
  )

glimpse(train)
```

We will use this same dataset for this entire assignment.

<ol start="2">
  <li>Use the code below to take 100 bootstrap samples of your data. Confirm that the result is a <code>tibble</code> with a <code>list</code> column of <code>resample</code> objects - each <code>resample</code> object is a bootstrap sample of the titanic dataset.</li>
</ol>

```{r}
# file_path <- '../data/homework9/train.csv'
# train <- read_csv(file_path)
# train
```
