---
title: "COMPSCIX 415.2 Homework 3B"
author: "Rachel Hollowgrass"
date: "2/20/2018"
output:
 html_document:
  self_contained: true
---

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
```

### Section 3.9.1

**Exercise 2:** What does 'labs()' do? Read the documentation.

From the [ggplot](http://ggplot2.tidyverse.org/reference/labs.html) docs, 'labs()' can specify the "lables" for a graph, including the overall title, and axes titles.

**Exercise 4:** _What does the plot below tell you about the relationship between city and highway mpg?_
The plot shows that the city/hwy relationship is generally linear.

_Why is_ 'coord_fixed()' _important?_
Without it, the units for the two axes are not the same.

_What does_ 'geom_abline()' _do?_
'geom_abline()' draws a line. Parameters such as y-intercept and slope are not specified, so it defaults to a line through the origin with slope of 1.

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()
```
