---
title: "COMPSCIX 415.2 Homework 3D"
author: "Rachel Hollowgrass"
date: "2/20/2018"
output:
 html_document:
  self_contained: true
---

```{r, warning = FALSE, message = FALSE}
library(nycflights13)
library(tidyverse)
```

### Section 5.2.4

**Exercise 1:** Find all flights that  

_1: Had an arrival delay of two or more hours_  

```{r}
filter(flights, arr_delay >= 120)
```


_2: Flew to Houston (IAH or HOU)_  

```{r}
filter(flights, dest %in% c('IAH', 'HOU'))
```


_3: Were operated by United, American, or Delta_  

```{r}
filter(flights, carrier %in% c('UA', 'AA', 'DL'))
```


_4: Departed in summer (July, August, and September)_  

```{r}
filter(flights, month %in% c(7, 8, 9))
```


_5: Arrived more than two hours late, but didn’t leave late_  

```{r}
filter(flights, arr_delay > 120, dep_delay <= 0)
```


_6: Were delayed by at least an hour, but made up over 30 minutes in flight_  

```{r}
filter(flights, dep_delay >= 60, (dep_delay - arr_delay) > 30)
```


_7: Departed between midnight and 6am (inclusive)_  

```{r}
filter(flights, dep_time >= 0, dep_time <= 6)
```

**Exercise 2:** Another useful dplyr filtering helper is 'between()'. What does it do? Can you use it to simplify the code needed to answer the previous challenges?  


**Exercise 3:** How many flights have a missing 'dep_time'? What other variables are missing? What might these rows represent?  


**Exercise 4:** Why is 'NA ^ 0' not missing? Why is 'NA | TRUE' not missing? Why is 'FALSE & NA' not missing? Can you figure out the general rule? ('NA * 0' is a tricky counterexample!)  

