---
title: "COMPSCIX 415.2 Homework 3D"
author: "Rachel Hollowgrass"
date: "2/20/2018"
output:
 html_document:
  self_contained: true
---

```{r, warning = FALSE, message = FALSE}
library(nycflights13)
library(tidyverse)
```

### Section 5.2.4

**Exercise 1:** Find all flights that  

_1: Had an arrival delay of two or more hours_  

```{r}
filter(flights, arr_delay >= 120)
```


_2: Flew to Houston (IAH or HOU)_  

```{r}
filter(flights, dest %in% c('IAH', 'HOU'))
```


_3: Were operated by United, American, or Delta_  

```{r}
filter(flights, carrier %in% c('UA', 'AA', 'DL'))
```


_4: Departed in summer (July, August, and September)_  

```{r}
filter(flights, month %in% c(7, 8, 9))
```


_5: Arrived more than two hours late, but didn’t leave late_  

```{r}
filter(flights, arr_delay > 120, dep_delay <= 0)
```


_6: Were delayed by at least an hour, but made up over 30 minutes in flight_  

```{r}
filter(flights, dep_delay >= 60, (dep_delay - arr_delay) > 30)
```


_7: Departed between midnight and 6am (inclusive)_  

```{r}
filter(flights, dep_time >= 0, dep_time <= 6)
```

**Exercise 2:** Another useful dplyr filtering helper is 'between()'. What does it do? Can you use it to simplify the code needed to answer the previous challenges?  

'between()' offers a more readable way of requesting values between two limits, inclusive. Questions 4 and 7 could have been written as:

> Question 4:  
> As is: filter(flights, month %in% c(7, 8, 9))  
> Rewritten: filter(flights, between(month, 7, 9))  

> Question 7:  
> As is: filter(flights, dep_time >= 0, dep_time <= 6)  
> Rewritten: filter(flights, between(dep_time, 0, 6))  

**Exercise 3:** How many flights have a missing 'dep_time'? What other variables are missing? What might these rows represent?  

There are 8,255 flights wihout a departure time. These flights may have been cancelled.

```{r}
filter(flights, is.na(dep_time))
```


**Exercise 4:**

_Why is 'NA ^ 0' not missing?_  

Any number to the 0th power is defined to be 1 (which would not be missing), with the exception of 0^0, which is not defined. Assuming that NA has a numeric value, If NA is defined to not be 0, then NA ^ 0 is 1.


_Why is 'NA | TRUE' not missing?_  

For any value X, 'X | TRUE' is TRUE. Therefore, 'NA | TRUE' is not missing.

_Why is 'FALSE & NA' not missing?_

For any value X, 'FALSE & X' is FALSE Therefore, 'FALSE & NA' is not missing.

_Can you figure out the general rule? ('NA * 0' is a tricky counterexample!)_  

If NA always has a numeric value and if NA is defined to not be 0, then NA could follow the rules for numerical values, such as:  
NA ^ 0 = 1  
0 / NA = 0  
NA * 0 = 0  

However, from my perspective, assuming that NA is **not** 0, or that it even is a number is assuming too much. 'NA' means that we do not know. If other values for a variable are all strings, I would assume that any missing value would also be a string if it were to be filled in later.


