---
title: "COMPSCIX 415.2 Homework 3E"
author: "Rachel Hollowgrass"
date: "2/20/2018"
output:
 html_document:
  self_contained: true
---

```{r, warning = FALSE, message = FALSE}
library(nycflights13)
library(tidyverse)
```

### Section 5.4.1

**Exercise 1:** Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.  

> select(flights, dep_time, dep_delay, arr_time, arr_delay)  
> select(flights, starts_with("dep_"), starts_with("arr_"))  
> select(flights, ends_with("delay"), matches("^d.._time"), matches("^ar._time"))
> select(flights, dep_time:dep_time, dep_delay:dep_delay, arr_time:arr_time, arr_delay:arr_delay)
> select(flights, -year, -month, -day, -sched_dep_time, -sched_arr_time, -carrier, -flight, -tailnum, -origin, -dest, -air_time, -distance, -hour, -minute, -time_hour)
> select(flights, one_of(c("dep_time","dep_delay","arr_time","arr_delay")))

**Exercise 2:** What happens if you include the name of a variable multiple times in a select() call?

R only selects the column once:

```{r}
select(flights, sched_dep_time, sched_dep_time, sched_dep_time)
```

**Exercise 3:** What does the one_of() function do? Why might it be helpful in conjunction with this vector?

> vars <- c("year", "month", "day", "dep_delay", "arr_delay")  

'one_of()' allows easy selection from a set of variables.

'one_of()' could be used in a subsequent 'select' statement, e.g., starting from the above statement  

> select(flights, one_of(vars))

**Exercise 4:** Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?

> select(flights, contains("TIME"))  

Yes, it surprised me because I expected it to be case sensitive. Apparently the default for select helpers is to be case insensitive. Here's a way to change that:  

```{r}
select(flights, contains("TIME", ignore.case = FALSE)) 
```
