---
title: "COMPSCIX 415.2 Homework 1"
author: "Rachel Hollowgrass"
date: "2/5/2018"
output: html_document
---

My Github repository for my assignments can be found at this URL: [Rachel Hollowgrass IDS HW 1](https://github.com/rachelhollowgrass/ids-hw-1)

### Answers to homework questions
**Question 1:** There are 23,018 observations and 10 variables in this data set.  
  
**Question 2:** Extract the region column and show only the unique values:  
    *region_col <- WorldCities$region*  
    *unique(region_col)*

**Question 3:** Unique entries from the country column using one line of code and two %>% operators:  
    *WorldCities %>% select(country) %>% unique()*  

**Question 4:** Variation on the histogram:  
    *WorldCities %>% ggplot(aes(x = population)) +*  
      *geom_histogram() +*  
      *xlab('Population per City') +*   
      *ylab('Number of Cities') +*  
      *ggtitle('Distribution of City Populations') +*  
      *theme_bw()*  


```{r setup, include=FALSE}
# Setting up
knitr::opts_chunk$set(echo = TRUE)
library(mdsr)
library(tidyverse)
# The following line kept causing errors, so I've commented it out.
# “‘{r load_packages, warning=FALSE, message=FALSE}
data(WorldCities)
```

``` {r}
# Exploring
# glimpse(WorldCities)
# WorldCities <- head(WorldCities, 200)
# country_col <- WorldCities$country
# unique(country_col)

# WorldCities %>% ggplot(aes(x = population)) + 
#   geom_histogram() +
#  xlab('City Population')


````

```` {r}
# Homework question 2
region_col <- WorldCities$region
unique(region_col)
````

```` {r}
# Homework question 3
WorldCities %>% select(country) %>% unique()
````

```` {r}
# Homework question 4
WorldCities %>% ggplot(aes(x = population)) + 
   geom_histogram() +
   xlab('Population per City') + 
   ylab('Number of Cities') + 
   ggtitle('Distribution of City Populations') + 
   theme_bw()
```