---
title: "COMPSCIX 415.2 Homework 7"
author: "Rachel Hollowgrass"
date: "3/20/2018"
output:
 html_document:
  self_contained: true
---

```{r, warning = FALSE, message = FALSE}
# load packages
library(tidyverse)
library(broom)
```


### Exercise 1  

_Load the train.csv dataset into R. How many observations and columns are there?_  

```{r}
file_path <- '../data/train.csv'
train <- read_csv(file_path)
```
There are:
<ul>
<li>1460 observations</li>
<li>80 columns of variables (not including the ID number)</li>
</ul>

### Exercise 2  

_Normally at this point you would spend a few days on EDA, but for this homework we will get right to fitting some linear regression models._  

_Our first step is to randomly split the data into train and test datasets. We will use a 70/30 split. There is an R package that will do the split for you, but let’s get some more practice with R and do it ourselves by filling in the blanks in the code below._  

```{r}
# When taking a random sample, it is often useful to set a seed so that
# your work is reproducible. Setting a seed will guarantee that the same
# random sample will be generated every time, so long as you always set the
# same seed beforehand
set.seed(29283)

# This data already has an Id column which we can make use of.
# Let's create our training set using sample_frac. Fill in the blank.
train_set <- train %>% sample_frac(.7)

# let's create our testing set using the Id column. Fill in the blanks.
test_set <- train %>% filter(!(train$Id %in% train_set$Id))
```

### Exercise 3  

_Our target is called <code>SalePrice</code>. First, we can fit a simple regression model consisting of only the intercept (the average of SalePrice). Fit the model and then use the broom package to_  

<ul>
<li>_take a look at the coefficient,_</li>
<li>_compare the coefficient to the average value of SalePrice, and_</li>
<li>_take a look at the R-squared._</li>
</ul>

_Use the code below and fill in the blanks._  

```{r}
# Fit a model with intercept only
mod_0 <- lm(SalePrice ~ 1, data = train_set)

# Double-check that the average SalePrice is equal to our model's coefficient
mean(train_set$SalePrice)
tidy(mod_0)

# Check the R-squared
glance(mod_0)
```

### Exercise 4   

_Now fit a linear regression model using <code>GrLivArea</code>, <code>OverallQual</code>, and <code>Neighborhood</code> as the features. Don't forget to look at <code>data_description.txt</code> to understand what these variables mean. Ask yourself these questions before fitting the model:_  

<ul>
<li>_What kind of relationship will these features have with our target?_</li>
<li>_Can the relationship be estimated linearly?_</li>
<li>_Are these good features, given the problem we are trying to solve?_</li>
</ul>

_After fitting the model, output the coefficients and the R-squared using the broom package._  

_Answer these questions:_  

<ul>
<li>_How would you interpret the coefficients on <code>GrLivArea</code> and <code>OverallQual</code>?_</li>
<li>_How would you interpret the coefficient on <code>NeighborhoodBrkSide</code>?_</li>
<li>_Are the features significant?_</li>
<li>_Are the features practically significant?_</li>
<li>_Is the model a good fit (to the training set)?_</li>
</ul>

