---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "Rachel Hollowgrass"
date: "3/6/2018"
output:
 html_document:
  self_contained: true
  toc: true
  toc_depth: 2
---

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
```

# The tidyverse packages (3 points)  

**1. Can you name which package is associated with each task below?**  

**Plotting:** ggplot

**Data munging/wrangling:** dplyr

**Reshaping (speading and gathering) data**: tidyr

**Importing/exporting data**: readr

**2. Now can you name two functions that you’ve used from each package that you listed above for these tasks?**  

**Plotting:**  
+ geom_point()
+ geom_boxplot()  

**Data munging/wrangling:**  
* filter()
* arrange()  

**Reshaping data**: 
* gather()
* spread()  

**Importing/exporting data** _(note that readRDS and saveRDS are base R functions)_: 
* read_csv()
* write_tsv()  

# R Basics (1.5 points)

**1. Fix this code _with the fewest number of changes possible_ so it works:**

```{r}
#My_data.name___is.too00ooLong! <- c( 1 , 2   , 3 )
```

