---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "Rachel Hollowgrass"
date: "3/6/2018"
output:
 html_document:
  self_contained: true
  toc: true
  toc_depth: 2
---

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
```

# The tidyverse packages (3 points)  

**1. Can you name which package is associated with each task below?**  

**Plotting:** <code>ggplot</code>  

**Data munging/wrangling:** <code>dplyr</code>  

**Reshaping (speading and gathering) data**: <code>tidyr</code>  

**Importing/exporting data**: <code>readr</code>  

**2. Now can you name two functions that you’ve used from each package that you listed above for these tasks?**  

**Plotting:**  
• <code>geom_point()</code>  
• <code>geom_boxplot()</code>  

**Data munging/wrangling:**  
• <code>filter()</code>  
• <code>arrange()</code>  

**Reshaping data**:  
• <code>gather()</code>  
• <code>spread()</code>  

**Importing/exporting data** _(note that readRDS and saveRDS are base R functions)_:  
• <code>read_csv()</code>  
• <code>write_tsv()</code>  

# R Basics (1.5 points)

**1. Fix this code _with the fewest number of changes possible_ so it works:**  

The single change is to remove the exclamation point from the end of the variable name:  

```{r}
# My_data.name___is.too00ooLong! <- c( 1 , 2   , 3 )
My_data.name___is.too00ooLong <- c( 1 , 2   , 3 )
```

**2. Fix this code so it works:**  

Changes:  
• Add a terminal single quote to the last item in the vector.  
• Change the "C" to lower case.  

```{r}
# my_string <- C('has', 'an', 'error', 'in', 'it)
my_string <- c('has', 'an', 'error', 'in', 'it')
```

**3. Look at the code below and comment on what happened to the values in the vector.**  

Comment: I assumed that the first, second and last items would have remained integers, but they were converted to strings. In a quick test, I see that unless all vector items are initially numberic, they are all converted to stings.   

```{r}
my_vector <- c(1, 2, '3', '4', 5)
my_vector

all_numeric_vector <- c(1, 2, 3, 4, 5)
all_numeric_vector

all_but_one_numeric_vector <- c(1, 2, '3', 4, 5)
all_but_one_numeric_vector
```

# Data import/export (3 points)

**1. Download the rail_trail.txt file from Canvas (in the Midterm Exam section here) and successfully import it into R. Prove that it was imported successfully by including your import code and taking a glimpse of the result.**  

**2. Export the file into an R-specific format and name it “rail_trail.rds”. Make sure you define the path correctly so that you know where it gets saved. Then reload the file. Include your export and import code and take another glimpse.**  

```{r}
# My_data.name___is.too00ooLong! <- c( 1 , 2   , 3 )
My_data.name___is.too00ooLong <- c( 1 , 2   , 3 )
```