---
title: "COMPSCIX 415.2 Homework 6"
author: "Rachel Hollowgrass"
date: "3/13/2018"
output:
 html_document:
  self_contained: true
---

```{r, warning = FALSE, message = FALSE}
library(mosaicData)
library(tidyverse)
```

### Exercise 1

Load the <code>Whickham</code> dataset (<code>data(Whickham)</code>). You will need to load the mosaicData package first, but I also included the data as an rds file on Canvas if you would rather download it there and load it with <code>readRDS()</code>.  

Look at the help file on this dataset to learn a bit about it.  

**1.** What variables are in this data set?

The variables in this data set are:
<ul>
<li><code>outcome</code></li>
<li><code>smoker</code></li>
<li><code>age</code></li>
</ul>

**2.** How many observations are there and what does each represent?

There are 1,314 observations. Each observation represents the age and tobacco smoking status of voting-age women from Whickham, UK in 1972-1974. The <code>outcome</code> represents a follow-up survey conducted 20 years later, indicating whether or not the woman was alive or dead.

**3.** Create a table (use the R code below as a guide) and a visualization of the relationship between smoking status and outcome, ignoring age. What do you see? Does it make sense?

I associate smoking with death, so I was surprised to see that the proportion of survivors ("alive") was about evenly split between smokers and non-smokers. I was even more surpised that more non-smokers were dead than smokers. I assume that factoring in age and years of smoking would shed some light on this.

```{r}
whickham2 <- Whickham %>% count(smoker, outcome)
whickham2
ggplot(whickham2) +
  geom_col(aes(x = outcome, y = n, fill = smoker), position = "stack") + 
 labs(x = "Outcome", y = "Number")
```
**4.** Recode the <code>age</code> variable into an ordered factor with three categories: age <= 44, age > 44 & age <= 64, and age > 64. Now, recreate visualization from above, but facet on your new age factor. What do you see? Does it make sense?

```{r}
whickham3 <- Whickham %>% mutate(age_fct = 
  factor(case_when(age <= 44 ~ 'Under 45',
                  age > 44 & age <= 64 ~ '45 to 64',
                  age > 64 ~ '65 and over'),
             levels = c('Under 45', '45 to 64', '65 and over')))
whickham4 <- whickham3 %>% count(smoker, outcome, age_fct)
whickham4
ggplot(whickham4) +
  geom_col(aes(x = outcome, y = n, fill = smoker), position = "stack") + 
  facet_wrap(~ age_fct, nrow = 8)
```

After factoring by age, it makes sense that more of the younger women (< 45) would be alive, and more of the older women (> 64) would be dead. For the older women, the majority of those still alive did not smoke (28 vs. 6). In addition, for older women, 15% of non-smokers were still alive (28 out of 193), while 12% of smokers were still alive (6 out of 50). Still, of the older women who have died, many more of them were non-smokers than smokers (65 to 44).

### Exercise 2

The Central Limit Theorem states that the sampling distribution of sample means is approximately Normal, regardless of the distribution of your population. For this exercise our population distribution will be a Gamma(1,2) distribution, and we’ll show that the sampling distribution of the mean is in fact normally distributed.

**1.** Generate a random sample of size n = 10000 from a gamma(1,2) distribution and plot a histogram or density curve. Use the code below to help you get your sample.

```{r}
n <- 10000
# look at ?rgamma to read about this function
gamma_samp <- tibble(x = rgamma(n, shape = 1, scale = 2))
gamma_samp %>% ggplot(aes(x)) + geom_histogram(bins = 200)
```
**2.** What is the mean and standard deviation of your sample? They should both be close to 2 because for a gamma distribution:
<ul>
<li>mean = shape x scale</li>
<li>variance = shape x scale^2</li>
</ul>

The mean and standard deviation of the sample vary each time the sample is drawn. Both have been approximately 2.

```{r}
gamma_samp <- tibble(x = rgamma(10000, shape = 1, scale = 2))
mean_samp <- gamma_samp %>% .[['x']] %>% mean()
sd_samp <- gamma_samp %>% .[['x']] %>% sd()
mean_samp
sd_samp
```

**3.** Pretend the distribution of our **population** of data looks like the plot above. Now take a sample of size n = 30 from a Gamma(1,2) distribution, plot the histogram or density curve, and calculate the mean and standard deviation.

```{r}
# 
```

**4.** Take a sample of size n = 30, again from the Gamma(1,2) distribution, calculate the mean, and assign it to a vector named mean_samp. Repeat this 10000 times!!!! The code below might help.

```{r}
# 
```
