---
title: "COMPSCIX 415.2 Homework 6"
author: "Rachel Hollowgrass"
date: "3/13/2018"
output:
 html_document:
  self_contained: true
---

```{r, warning = FALSE, message = FALSE}
library(mosaicData)
library(tidyverse)
```

### Exercise 1

Load the <code>Whickham</code> dataset (<code>data(Whickham)</code>). You will need to load the mosaicData package first, but I also included the data as an rds file on Canvas if you would rather download it there and load it with <code>readRDS()</code>.  

Look at the help file on this dataset to learn a bit about it.  

**1.** What variables are in this data set?

The variables in this data set are:
<ul>
<li><code>outcome</code></li>
<li><code>smoker</code></li>
<li><code>age</code></li>
</ul>

**2.** How many observations are there and what does each represent?

There are 1,314 observations. Each observation represents the age and tobacco smoking status of voting-age women from Whickham, UK in 1972-1974. The <code>outcome</code> represents a follow-up survey conducted 20 years later, indicating whether or not the woman was alive or dead.

**3.** Create a table (use the R code below as a guide) and a visualization of the relationship between smoking status and outcome, ignoring age. What do you see? Does it make sense?

I associate smoking with death, so I was surprised to see that the proportion of survivors ("alive") was about evenly split between smokers and non-smokers. I was even more surpised that more non-smokers were dead than smokers. I assume that factoring in age and years of smoking would shed some light on this.

```{r}
whickham2 <- Whickham %>% count(smoker, outcome)
whickham2
ggplot(whickham2) +
  geom_col(aes(x = outcome, y = n, fill = smoker), position = "stack") + 
  labs(x = "Outcome", y = "Number")
```
**4.** Recode the <code>age</code> variable into an ordered factor with three categories: age <= 44, age > 44 & age <= 64, and age > 64. Now, recreate visualization from above, but facet on your new age factor. What do you see? Does it make sense?

```{r}
whickham3 <- Whickham %>% mutate(age_fct = 
  factor(case_when(age <= 44 ~ 'Under 45',
                  age > 44 & age <= 64 ~ '45 to 64',
                  age > 64 ~ '65 and over'),
             levels = c('Under 45', '45 to 64', '65 and over')))
whickham4 <- whickham3 %>% count(smoker, outcome, age_fct)
whickham4
ggplot(whickham4) +
  geom_col(aes(x = outcome, y = n, fill = smoker), position = "stack") + 
  facet_wrap(~ age_fct, nrow = 8)
```

After factoring by age, it makes sense that more of the younger women (< 45) would be alive, and more of the older women (> 64) would be dead. For the older women, the majority of those still alive did not smoke (28 vs. 6). In addition, for older women, 15% of non-smokers were still alive (28 out of 193), while 12% of smokers were still alive (6 out of 50). Still, of the older women who have died, many more of them were non-smokers than smokers (65 to 44).

### Exercise 2

The Central Limit Theorem states that the sampling distribution of sample means is approximately Normal, regardless of the distribution of your population. For this exercise our population distribution will be a Gamma(1,2) distribution, and we’ll show that the sampling distribution of the mean is in fact normally distributed.

**1.** Generate a random sample of size n = 10000 from a gamma(1,2) distribution and plot a histogram or density curve. Use the code below to help you get your sample.

```{r}
n <- 10000
# look at ?rgamma to read about this function
gamma_samp <- tibble(x = rgamma(n, shape = 1, scale = 2))
gamma_samp %>% ggplot(aes(x)) + geom_histogram(bins = 200, fill = "#493BB4")
```
**2.** What is the mean and standard deviation of your sample? They should both be close to 2 because for a gamma distribution:
<ul>
<li>mean = shape x scale</li>
<li>variance = shape x scale^2</li>
</ul>

The mean and standard deviation of the sample vary each time the sample is drawn. Both have been approximately 2.

```{r}
gamma_samp <- tibble(x = rgamma(10000, shape = 1, scale = 2))
mean_samp <- gamma_samp %>% .[['x']] %>% mean()
sd_samp <- gamma_samp %>% .[['x']] %>% sd()
mean_samp
sd_samp
```

**3.** Pretend the distribution of our **population** of data looks like the plot above. Now take a sample of size n = 30 from a Gamma(1,2) distribution, plot the histogram or density curve, and calculate the mean and standard deviation.

```{r}
population <- tibble(x = rgamma(10000, shape = 1, scale = 2))
sample_size = 30
population_sample <- sample_n(population, sample_size)
# population_sample
ggplot(population_sample) +
  geom_histogram(aes(x), fill = "#4C79B4")
mean_pop_samp <- population_sample %>% .[['x']] %>% mean()
sd_pop_samp <- population_sample %>% .[['x']] %>% sd()
mean_pop_samp
sd_pop_samp
```

**4.** Take a sample of size n = 30, again from the Gamma(1,2) distribution, calculate the mean, and assign it to a vector named mean_samp. Repeat this 10000 times!!!! The code below might help.

**5.** Make a histogram of your collection of means from above (<code>mean_samp</code>).

**6.** Calculate the mean and standard deviation of all of your sample means.

```{r}
# create a vector with 10000 NAs
mean_samp <- rep(NA, 10000)

# start a loop
for(i in 1:10000) {
  g_samp <- rgamma(30, shape = 1, scale = 2)
  mean_samp[i] <- mean(g_samp)
}
# Convert vector to a tibble
mean_samp <- tibble(mean_samp)
# I could not find a way for ggplot to work with this without a variable (column) name.
names(mean_samp)[1]<-"x"
mean_samp %>% ggplot(aes(x)) + geom_histogram(fill = "#18B4B4")

mean_samp_mean <- mean_samp %>% .[['x']] %>% mean()
mean_samp_sd <- mean_samp %>% .[['x']] %>% sd()
mean_samp_mean
mean_samp_sd
```

**7.** Did anything surprise you about your answers to #6?

The mean was around 2, as expected. But the standard deviation has ranged between .35 and .38. I expected it to be around 2.

**8.** According to the Central Limit Theorem, the mean of your sampling distribution should be very close to 2, and the standard deviation of your sampling distribution should be close to σn‾√=230‾‾‾√=0.365.  

Repeat #4-#6, but now with a sample of size n = 300 instead. Do your results match up well with the theorem?

Yes, the results match up with the theorem.

**Expected values:**  
<ul>
<li>mean = 2.0</li>
<li>sd =   0.1154701</li>
</ul>


**One result:**  
<ul>
<li>mean = 1.998485</li>
<li>sd = 0.1144379</li>
</ul>

```{r}
# create a vector with 10000 NAs
mean_300_samp <- rep(NA, 10000)

# start a loop
for(i in 1:10000) {
  g_300_samp <- rgamma(300, shape = 1, scale = 2)
  mean_300_samp[i] <- mean(g_300_samp)
}
# Convert vector to a tibble
mean_300_samp <- tibble(mean_300_samp)
names(mean_300_samp)[1]<-"x"
mean_300_samp %>% ggplot(aes(x)) + geom_histogram(fill = "#18B4B4")

mean_300_mean <- mean_300_samp %>% .[['x']] %>% mean()
mean_300_sd <- mean_300_samp %>% .[['x']] %>% sd()
mean_300_mean
mean_300_sd
```