---
title: "COMPSCIX 415.2 Homework 6"
author: "Rachel Hollowgrass"
date: "3/13/2018"
output:
 html_document:
  self_contained: true
---

```{r, warning = FALSE, message = FALSE}
library(mosaicData)
library(tidyverse)
```

### Exercise 1

Load the <code>Whickham</code> dataset (<code>data(Whickham)</code>). You will need to load the mosaicData package first, but I also included the data as an rds file on Canvas if you would rather download it there and load it with <code>readRDS()</code>.  

Look at the help file on this dataset to learn a bit about it.  

**1.** What variables are in this data set?

The variables in this data set are:
<ul>
<li><code>outcome</code></li>
<li><code>smoker</code></li>
<li><code>age</code></li>
</ul>

**2.** How many observations are there and what does each represent?

There are 1,314 observations. Each observation represents the age and tobacco smoking status of voting-age women from Whickham, UK in 1972-1974. The <code>outcome</code> represents a follow-up survey conducted 20 years later, indicating whether or not the woman was alive or dead.

**3.** Create a table (use the R code below as a guide) and a visualization of the relationship between smoking status and outcome, ignoring age. What do you see? Does it make sense?

```{r}
Whickham %>% count( outcome , smoker )
```
