---
title: "COMPSCIX 415.2 Homework 2A"
author: "Rachel Hollowgrass"
date: "2/13/2018"
output:
 html_document:
  self_contained: true
---

```{r}
library(tidyverse)
```

### Section 3.2.4

**Exercise 1:** Without a geom, giving ggplot only a data frame results in a gray rectangle because neither the axes nor the presentation style have been specified.

```{r}
ggplot(data = mpg)
```

**Exercise 2:** The mpg data frame has 234 rows and 11 columns.

```{r}
?mpg
```

**Exercise 3:** The 'drv' variable has three values: {'f','r','4']. It describes whether a vehicle is front-, rear- or 4-wheel drive. 

```{r}
?mpg
```

**Exercise 4:** Plot of 'hwy' vs. 'cyl': 

```{r}
ggplot(data = mpg) + 
geom_point(mapping = aes(x = hwy, y = cyl))
```

**Exercise 5:** Plot of 'class' vs. 'drv': This plot has limited usefulness because each class of car may have multple models and/or years with the same 'drv' value. Adding 'position = "jitter"' to the mapping would reveal the hidden points.

```{r}
ggplot(data = mpg) + 
geom_point(mapping = aes(x = class, y = drv))
```

