title: "COMPSCIX 415.2 Homework 2D"
author: "Rachel Hollowgrass"
date: "2/13/2018"
output:
 html_document:
  self_contained: true
---

```{r}
library(tidyverse)
```

### Section 3.6.1

**Exercise 1:** What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?

* line chart: 'geom_line()'
* boxplot: 'geom_boxplot()'
* histogram: 'geom_histogram()'
* area chart: 'geom_area()'

**Exercise 2:** Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.

I think it will plot points as well as a smooth line that represents the nonlinear least-squares regression.

After running the code, my prediction was in the right direction, but the surprise was that there are three curves: one for each value of 'drv'.

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + geom_point() +
  geom_smooth(se = FALSE)
```

**Exercise 3:** Three questions:

_What does show.legend = FALSE do?_ It disables the rendering of a legend.

_What happens if you remove it?_ The legend for the last-specified aesthetic is visible. 

_Why do you think I used it earlier in the chapter?_ Multiple aesthetics were in use, and a single, particular legend was the best to represent them.

**Exercise 4:** What does the se argument to geom_smooth() do?

It shows or hides the [confidence interval](http://www.sthda.com/english/wiki/print.php?id=188) around the smooth regression line.

**Exercise 5:** Will these two graphs look different? Why/why not?

They will look the same.

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() +
  geom_smooth()
```

```{r}
ggplot() +
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
```
