title: "COMPSCIX 415.2 Homework 2D"
author: "Rachel Hollowgrass"
date: "2/13/2018"
output:
 html_document:
  self_contained: true
---

```{r}
library(tidyverse)
```

### Section 3.6.1

**Exercise 1:** What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?

* line chart: 'geom_line()'
* boxplot: 'geom_boxplot()'
* histogram: 'geom_histogram()'
* area chart: 'geom_area()'

**Exercise 2:** Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.

I think it will plot points as well as a smooth line that represents the nonlinear least-squares regression.

After running the code, my prediction was in the right direction, but the surprise was that there are three curves: one for each value of 'drv'.

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + geom_point() +
  geom_smooth(se = FALSE)
```

**Exercise 3:** What does show.legend = FALSE do? What happens if you remove it? Why do you think I used it earlier in the chapter?

```{r}
```

**Exercise 4:** What does the se argument to geom_smooth() do?

```{r}
```

**Exercise 5:** Will these two graphs look different? Why/why not?
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + geom_point() +
geom_smooth()
ggplot() +
geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))

```{r}
```

**Exercise 6:** Recreate the R code necessary to generate the following graphs.

```{r}
```
