---
title: "COMPSCIX 415.2 Homework 4A"
author: "Rachel Hollowgrass"
date: "2/27/2018"
output:
 html_document:
  self_contained: true
---

```{r, warning = FALSE, message = FALSE}
library(nycflights13)
library(tidyverse)
```

### Section 5.6.7

**Exercise 2:** Come up with another approach that will give you the same output as 'not_cancelled %>% count(dest)' and 'not_cancelled %>% count(tailnum, wt = distance)' (without using count()).

```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay)) %>% group_by(dest) %>% summarise(n())
not_cancelled
```

```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay)) %>% group_by(tailnum, wt = distance) %>% summarise(n())
not_cancelled
```

**Exercise 4:** Look at the number of cancelled flights per day.

```{r}
# Flights that were cancelled each day:
cancelled <- flights %>% 
  filter(is.na(dep_delay), is.na(arr_delay)) %>% group_by(year, month, day) %>% summarise(n())
cancelled
```

_Is there a pattern?_ ••• 

_Is the proportion of cancelled flights related to the average delay?_

It does not appear to be.

```{R}
flights %>% 
  group_by(year, month, day) %>% 
  summarise(cancelled_to_non_cancelled = sum(is.na(arr_delay)) / sum(!is.na(arr_delay)), 
  average_delay = mean(arr_delay, na.rm = TRUE))
```

**Exercise 5:** Which carrier has the worst delays?

F9, with an average delay of 21.9, has the worst delays.

```{r}
by_carrier <- group_by(flights, carrier) 
by_delay <- summarise(by_carrier,
  count = n(),
  delay = mean(arr_delay, na.rm = TRUE)
) %>% count(delay, carrier, sort = TRUE)

by_delay
```

_Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about flights %>% group_by(carrier, dest) %>% summarise(n()))_ ••• 


**Exercise 6:** What does the sort argument to 'count()' do? When might you use it?

The sort argument, if true, sorts the first argument in order of the count() results.

```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay)) %>% count(dest, sort = TRUE)
not_cancelled
```
